---
title: "Linmods package"
description: "Description for the Linmods-package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linmods package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Introduction

This post a introduction to the package `Linmods`. The package can be used to apply multiple linear regression.
The package `Linmods` has several methods which are used to print tables and components which belongs to the regression model.`linreg` returns a list which contatins several statistics from the applied linear regression model. The returned list is of class "linreg". The `print()`method outputs the formula and the coefficients of the method.
The `plot()` is used to plot a scatterplot, residuals versus fitted values, and a scale-location plot.
`resid()` function returns the residuals *e*. `pred()`returns the predicted values and `coef()` returns the coefficients as a named vector.

## Examples using "iris"
```{r,results='hide'}
example1<-Linmods::linreg(Petal.Length~Sepal.Length+Petal.Width,data=iris)
```

```{r}
class(example1)
```
We did run a linear regression with the "linreg" function in the "Linmods" package and did get a list of class "linreg" as result.

### Print()
`Print()` is a method of the "linreg" function. When you print a object of class "linreg", you will get a output with the formula of the model and the coefficients of the model.
```{r}
print(example1)
```


### Plot()
The `plot()` is used to plot a scatterplot, residuals versus fitted values, and a scale-location plot.
```{r,eval=FALSE}
plot(example1)
```

### resid()
Using the `resid()` method of class "linreg" you can get the residuals of the model.
```{r,eval=FALSE}
resid(example1)
```

### pred()
Using the `resid` method of class "linreg" you can get the residuals of the model.
```{r,eval=FALSE}
pred(example1)
```

### coef()
`coef()` gives you the coefficients as a named vector.
```{r,eval=TRUE}
coef(example1)
```

### summary()

`summary()` can be used like:

```{r,eval=TRUE}
summary(example1)
```

